---
title: "Pilgrim_Bank_B_Case_Study"
author: "Whitney Chu"
date: "02/10/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Install Packages
```{r}
library(tidyverse)    
library(e1071)  
library(RColorBrewer)
library(dplyr)
library(caTools)

```

#Read and Import Pilgrim Bank Data
```{r}
PBD <- read.csv("PilgrimDataExt.csv")
```

#Preview Dataset
```{r}
# Preview the head and summary of the dataset
head(PBD)
summary(PBD)
dim(PBD)
```


#Create Target Variable
```{r}
# create a column for customer retention (target variable)
names(PBD)
PBD <- data.frame(PBD)
PBD$Customer_Retention <- ifelse(PBD$X9Online == 1 & PBD$X0Online == 1, 0, 1)
names(PBD)
```

#Replace NA/Missing values
```{r}
#Replacing with median 
PBD <- as.data.frame(impute(PBD, what = c("median")))
```


#Create training and test set
```{r}
# 75% Train and 25% Test
rows <- c(1:nrow(PBD))
split <- sample(rows, size = (nrow(PBD)/(4)))
train <- PBD[-split, ]
test <- PBD[split,]
nrow(train)
nrow(test)
```


#Generate Classifier

##Create a model with logistic regression
```{r}
train.mod1 <- glm(formula = Customer_Retention ~ X9Online +X9Age + X9Inc + X9Profit + X9Tenure+ X9Billpay, data = train, family = "binomial")
summary(train.mod1)
```



##Create a model Support Vector Machine (SVM)
```{r}
# Fitting SVM to the Training set 
train.mod2 = svm(formula = Customer_Retention ~ X9Online +X9Age + X9Inc + X9Profit + X9Tenure + X9Billpay, 
				data = train,kernel = 'linear') 
```


#Assess Error

Assessment of the Training error and Testing Error.

##Training Error for logistic regression
```{r}
predict.ret1 <- predict(train.mod1,train)
pred <- ifelse(predict.ret1 > 0.5, "1", "0")
mean(train$Customer_Retention!=pred)
table(pred,train$Customer_Retention)
```


##Training Error for SVM
```{r}
predict.ret2 <- predict(train.mod2,train)
pred <- ifelse(predict.ret2 > 0.5, "1", "0")
mean(train$Customer_Retention!=pred)
table(pred, train$Customer_Retention)
```

##Testing Error for logistic regression
```{r}
predict.ret1 <- predict(train.mod1,test)
pred <- ifelse(predict.ret1 > 0.5, "1", "0")
mean(test$Customer_Retention!=pred)
table(pred, test$Customer_Retention)
```


##Testing Error for SVM
```{r}
predict.ret2 <- predict(train.mod2,test)
pred <- ifelse(predict.ret2 > 0.5, "1", "0")
mean(test$Customer_Retention!=pred)
table(pred, test$Customer_Retention)
```












